Template for indicator documentation

### 2022-09-20 naturtype.Rmd

**Naturlig åpne områder under skoggrensa:**

@@

**Semi-naturlig mark**

@@

**Våtmark**

@@

@@

```{r, eval=F}
exp$ninkartleggingsenheter3 <- unlist(exp$ninkartleggingsenheter3)
#names(exp)[1] <- "ID" # Field name too long
saveRDS(exp, "/data/Egenutvikling/41001581_egenutvikling_anders_kolstad/data/Mdir_Naturtyper_cleanedALK.rds")

>>>>

### Naturlig åpne områder under skoggrensa

@@

### Semi-naturlig mark

@@

### Våtmark

@@

### Areal 
Same type of analysis as above, but focusing onthe accumalitive mapped rea.
```{r, fig.cap="Total mapped are for each combination of main ecosystem and NiN main type (after data set cleaning)"}
dat_red_tally_area <- stats::aggregate(data = dat_red4,
                                 area~hovedøkosystem+ninkartleggingsenheter3, FUN = sum)
names(dat_red_tally_area)[3] <- "area_m2"
dat_red_tally_area$area_km2 <- drop_units(dat_red_tally_area$area_m2/10^6)
ggplot(dat_red_tally_area[dat_red_tally_area$hovedøkosystem %in% target,],
       aes(x = ninkartleggingsenheter3,
               y = area_km2))+
  geom_bar(
           fill="grey",
           colour="black",
           stat="identity")+
  coord_flip()+
  theme_bw(base_size = 12)+
  labs(y = "Total mapped area (km/2)",
       x = "NiN main types")+
    facet_wrap("hovedøkosystem",
             scales = "free",
             ncol = 3)
```

@@

```{r, eval=F}
exp$ninkartleggingsenheter3 <- unlist(exp$ninkartleggingsenheter3)
saveRDS(exp, "/data/Egenutvikling/41001581_egenutvikling_anders_kolstad/data/Mdir_Naturtyper_cleanedALK.rds")
